% Master bullet bank. Use these markers so the parser can group bullets by role.
%
% Section marker (roles that follow belong to this section until the next marker):
%   %%% SECTION: <section heading, e.g. Experience, Projects, Leadership>
%
% Role block format:
%   %%% ROLE_ID: <unique_id>
%   %%% COMPANY: <company name, or project name for Projects section>
%   %%% TITLE: <job title, or tech stack for Projects section>
%   %%% DATES: <e.g. Jun 2023 -- Aug 2023>
%   %%% LOCATION: <e.g. San Francisco, CA; leave blank for projects>
%   %%% SIZE: big | small     (big = up to 4 bullets, small = up to 3)
%   <bullet 1>
%   <bullet 2>
%   %%% END_ROLE
%
% Skills block format (one block total):
%   %%% SKILLS_START
%   %%% ROW: <row name, e.g. Languages>
%   skill1, skill2, skill3
%   %%% SKILLS_END


%%% SECTION: Experience

%%% ROLE_ID: ibm
%%% COMPANY: International Business Machines (IBM)
%%% TITLE: Incoming Software Development Intern
%%% DATES: May 2026 -- Aug. 2026
%%% LOCATION: Durham, NC
%%% SIZE: small
%%% END_ROLE


%%% ROLE_ID: progroup_swe_intern
%%% COMPANY: ProGroup
%%% TITLE: Software Engineer Intern
%%% DATES: Dec. 2025 -- Present
%%% LOCATION: Irvine, CA
%%% SIZE: big
Cut costs by 70\% by migrating an onboarding app from Microsoft Power Apps to MySQL, Node.js, and AWS.
Designed an onboarding platform for 400+ HR professionals and new hires across multiple organizations.
Automated email workflows and task monitoring for onboarding, saving 8 hours for each team member per week.
Built a CI/CD pipeline to automate AWS deployments, reducing deployment times from 15 minutes to 2 minutes.
Deployed and managed cloud infrastructure leveraging AWS EC2, Lambda, EventBridge, IAM, and SNS.
Implemented Redis caching on high-traffic endpoints, reducing latency by 80\% and decreasing backend load.
Conducted peer code reviews and incorporated customer feedback loops to iteratively improve product quality.
%%% END_ROLE


%%% ROLE_ID: uci_python_ta
%%% COMPANY: University of California, Irvine
%%% TITLE: Python Teaching Assistant
%%% DATES: Jan. 2026 -- Present
%%% LOCATION: Irvine, CA
%%% SIZE: small
Instructed 200 students on Python concepts including OOP, testing, generators, multithreading, and scripting.
%%% END_ROLE


%%% ROLE_ID: thai_oil_data_science_intern
%%% COMPANY: Thai Oil
%%% TITLE: Data Science Intern
%%% DATES: Jun. 2024 -- Sep. 2024
%%% LOCATION: Bangkok, Thailand
%%% SIZE: small
Built an RNN classifying 7 pipe failure types from 43 GB of sensor time-series data, achieving 89\% accuracy.
Designed ETL pipelines to ingest, normalize, and standardize raw sensor data across refinery data sources.
Deployed model to AWS SageMaker and S3 for scalable cloud inference, eliminating manual diagnostic workflows.
Reduced maintenance costs by 15\% through the automation of pipe fault diagnostic across operations.
%%% END_ROLE


%%% SECTION: Projects


%%% ROLE_ID: squadwork
%%% COMPANY: Squadwork
%%% TITLE: TypeScript, Node.js, Redis, WebSockets, JWT, Docker, AWS ECS
%%% DATES: Jun. 2025 -- Present
%%% LOCATION:
%%% SIZE: big
Implemented real-time WebSocket chat with PostgreSQL persistence and Redis caching for recent message logs.
Layered Redis caching on session tokens and task queries, cutting average API latency by 75\% on vital endpoints.
Dispatched chat and task notifications through AWS SES and SMS for users with linked phone numbers.
Tested the full stack by simulated 32,000 mixed-use RPS, validating stability under peak concurrent traffic.
Automated CI/CD pipelines on EC2, cutting deployment times, then migrated to EKS for orchestration.
Built a full-stack team manager with shared and nested tasks, real-time chat, and an AI brainstorming agent.
Architected RESTful APIs with JWT auth using rotating access/refresh tokens for stateless session management.
%%% END_ROLE


%%% ROLE_ID: fabflix
%%% COMPANY: Fabflix
%%% TITLE: Java, MySQL, Tomcat, Kubernetes, Docker, AWS, Distributed Systems
%%% DATES: Jan. 2026 -- Mar. 2026
%%% LOCATION:
%%% SIZE: big
Served 65,000+ movies with sub-150ms responses using MySQL replication, connection pooling, and caching.
Deployed Dockerized microservices on AWS EKS with autoscaling, health checks, and zero-downtime rollouts.
Implemented substring, fuzzy, and full-text search over normalized MySQL tables for movies, stars, and genres.
Configured MySQL master-slave replication and load balancing to distribute reads and ensure write consistency.
Built autocomplete search with MySQL UDFs and Redis caching to reduce redundant database queries.
Orchestrated microservices on Kubernetes/EKS for independent scaling, fault isolation, and rolling deployments.
%%% END_ROLE


%%% ROLE_ID: ai_native_doc_editor
%%% COMPANY: AI Native Document Editor
%%% TITLE: TypeScript, Node.js, OpenAI API, WebSockets, PostgreSQL
%%% DATES: Oct. 2025 -- Dec. 2025
%%% LOCATION:
%%% SIZE: small
Built a real-time collaborative text editor with WebSockets, enabling multiple users to edit docs simultaneously.
Streamed OpenAI API requests with debounced input handling for text completion, optimizing API calls.
Designed granular read/write permissions, allowing users to selectively share documents with collaborators.
Implemented OAuth 2.0 for secure third-party authentication and session management.
%%% END_ROLE


%%% ROLE_ID: search_engine
%%% COMPANY: Search Engine
%%% TITLE: TypeScript, Node.js, OpenAI API, WebSockets, PostgreSQL
%%% DATES: Oct. 2025 -- Dec. 2025
%%% LOCATION:
%%% SIZE: small
Built a scalable Python web-crawling pipeline ingesting 60,000+ documents from JSON and HTML archives.
Designed tokenization with lowercasing, non-alphanumeric splitting, stop-word filtering, and stemming.
Developed weighted TF scoring with field weights for body, title, and headings, normalized by document length.
Compressed inverted index posts with variable-byte encoding for doc-ID deltas on a 60,000+ document corpus.
Built a PageRank pipeline using 50-iteration power iteration with 0.85 damping over a 60,000+ node URL graph.
Engineered an LRU-cached postings reader with varbyte decoding and vocab-offset seeks for low-latency queries.
%%% END_ROLE




%%% ROLE_ID: c_shell
%%% COMPANY: Shell in C
%%% TITLE: TypeScript, Node.js, OpenAI API, WebSockets, PostgreSQL
%%% DATES: Oct. 2025 -- Dec. 2025
%%% LOCATION:
%%% SIZE: small
Built an interactive Unix-style shell in C supporting core filesystem commands such as cd, pwd, and mkdir.
Implemented parsing and input handling to process terminal commands through a continuous execution loop.
Developed path resolution logic for relative paths, parent-directory navigation, and working directory updates.
Added error handling for bad commands, missing arguments, and nonexistent directories to improve reliability.
Used POSIX filesystem calls to create directories, change working directories, and retrieve path information.
%%% END_ROLE


%%% ROLE_ID: wildfire_watch
%%% COMPANY: Wildfire Watch
%%% TITLE: TypeScript, Node.js, OpenAI API, WebSockets, PostgreSQL
%%% DATES: Oct. 2025 -- Dec. 2025
%%% LOCATION:
%%% SIZE: small
Built a serverless fire safety app with AWS Lambda, Kinesis, DynamoDB, EventBridge, CloudFormation, and SNS.
Created Lambda functions to ingest wildfire, weather, and satellite data from NOAA, NASA, and CAL FIRE.
Automated recurring data ingestion with EventBridge scheduled triggers to keep prediction inputs updated.
Provisioned serverless AWS resources with CloudFormation templates to improve deployment consistency.
%%% END_ROLE


%%% SKILLS_START
%%% ROW: Languages
TypeScript, JavaScript, Python, Java, SQL, C++, HTML/CSS
%%% ROW: Frameworks \& Libraries
Node.js, Express, React, Next.js, FastAPI, Flask, Prisma, Tomcat
%%% ROW: Databases \& Caching
MySQL, PostgreSQL, Redis
%%% ROW: Cloud \& DevOps
AWS (ECS, EKS, EC2, Lambda, S3), GCP, Docker, Kubernetes, CI/CD, GitHub Actions, Git
%%% ROW: Testing \& Tools
Jest, Supertest, OAuth 2.0, JWT
%%% SKILLS_END



